ZCB Pricing

### 2018-07-24 ZCB Pricing .Rmd
Extra stuff

explicit <- function(alpha,beta,sigma,r,I){

@@

dt = 1/length(I) # length of each time sub-interval

@@

count <- 0 # set up count variable
for (i in rev(I)){ # rev is the reverse order of the time partition | i corresponds to the columns of the lattice
  count <- count+1 # keeping track of loop
  for (j in (1+count):(nr-count)){ # j corresponds to the rows of the lattice
    pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr) # up value
    pm <- 1/dt -sigma^2/(dr^2) # middle value
    pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) # down value
    V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
  }

@@

V[(nr+1)/2,1]
}

explicit(0.08,0.8,0.005,0.05,1:10)

@@

implicit <- function(alpha,beta,sigma,r,I,J){
  # I = partition of time interval
  # J = partition of short rate variable

@@

  dr <- J[2] - J[1] #length of each sub-interval across J
  dt <- 1/length(I) #length of each sub-interval across I

@@

R <- implicit(0.08,0.8,0.005,0.05,1:100,seq(-0.3,0.5,0.01))

@@

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
  }
plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```

@@

CN <- function(alpha, beta, sigma, r, I, J){
  # I = partition of time interval
  # J = partition of short rate interval

@@

  dr <- J[2] - J[1]
  dt <- 1/X

@@

G <- CN(0.08,0.8,0.005,0.05, I=1:100, J = seq(-0.3,0.5,0.01))

>>>>

explicit <- function(alpha,beta,sigma,r,I,T){

@@

dt = T/length(I) # length of each time sub-interval

@@

count <- 0 # set up count variable
for (i in rev(I)){ # rev is the reverse order of the time partition | i corresponds to the columns of the lattice
  count <- count+1 # keeping track of loop
  for (j in (1+count):(nr-count)){ # j corresponds to the rows of the lattice
    pu <- dt*(sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr)) # up value
    pm <- 1 - (sigma^2*dt)/(dr^2) # middle value
    pd <- dt*(sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr)) # down value
    V[j,i] <- ((1+J[nr-j]*dt)^(-1))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
  }

@@

V[(nr+1)/2,1]

X = explicit(0.08,0.8,0.005,0.03,1:50,T=1)
Z <- bond_price(0.08,0.8,0.005,0,1,0.03)

@@

implicit <- function(alpha,beta,sigma,r,I,J,T){
  # I = partition of time interval
  # J = partition of short rate variable

@@

  dr <- J[2] - J[1] #length of each sub-interval across J
  dt <- T/length(I) #length of each sub-interval across I

@@

R <- implicit(0.08,0.8,0.005,0.05,1:100,seq(-0.3,0.5,0.01),T=5)

@@

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
  }
plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```

@@

CN <- function(alpha, beta, sigma, r,T, I, J){
  # I = partition of time interval
  # J = partition of short rate interval

@@

  dr <- J[2] - J[1]
  dt <- T/X

@@

G <- CN(0.08,0.8,0.005,0.05, T=5, I=1:365, J = seq(-0.3,0.5,0.01))
